---
title: "1_conspiracy"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r message=FALSE, warning=FALSE}
# load libraries
if (!require("pacman")){
  install.packages("pacman")
}
pacman::p_load(tidyverse, 
               rio, 
               psych, 
               car,
               lavaan,
               sirt,
               here)
# set the current directory
here::i_am('README.md')
here::here()
#memory.limit(size=56000) #you might have to increase your memory limit
```


# Data + variables          

  Load clean data (from qualtrics). For codebook see: https://osf.io/gcek7/
  
```{r message=FALSE, warning=FALSE}
# load data
dat <- import(here("_cleandata/Final_COVIDiSTRESS_Vol2_cleaned.csv")) 

# rename education levels
dat$education[dat$education == "University degree (e.g., MA, MSc, BA, BSc)"] <- "University degree"
dat$education[dat$education == "Some University or equivalent \r\n(still ongoing, or completed a module or more, but did not graduate)"] <- "Some University"
```  
* focusing on conspiracy items
* Extracting data only from where language n ≥ 100
* set variables of interest

```{r message=FALSE, warning=FALSE}
# set variables of interest
variables <- c('conspirational_think_1','conspirational_think_2',
          'conspirational_think_3','conspirational_think_4')

# extract only columns of interest for measurement invariance test
# language and conspiracy items
dat_consp <- dat %>% dplyr::select(UserLanguage, #subset df
                        contains("conspirational_think"),
                        -contains("NAppl"))
# drop nas
dat_consp <- na.omit(dat_consp)

# filter out languages where N < 100
# let's move on to MI test across languages
table(dat_consp$UserLanguage)
# shall be >= 100
# extract 24 languages where N >= 100
n.langs <- table(dat_consp$UserLanguage)
list.langs <- labels(n.langs)[[1]]
langs.include <- list.langs[n.langs>=100]
n.include <- n.langs[n.langs>=100]


# extract data
for (i in 1:length(langs.include)){
  if (i == 1){
    dat_mi <- dat_consp[dat_consp$UserLanguage == langs.include[i],]
  }else{
    current <- dat_consp[dat_consp$UserLanguage == langs.include[i],]
    dat_mi <- rbind(dat_mi,current)
  }
}
# final N = 12143 from 24 languages
```

* do meausurement invariance test
```{r message=FALSE, warning=FALSE}
# cronbach's alpha = good
psych::alpha(dat_mi[,variables])

# model setting
cfa.model<-'
CONSP =~ conspirational_think_1 + conspirational_think_2+
  conspirational_think_3 + conspirational_think_4'
indices <- c('rmsea','srmr','cfi','tli')

# configural invariance
# DWLS preferred with 5+ categories (Christine DiStefano & Grant B. Morgan 2014)
fit.configural <- cfa(cfa.model, dat_mi, estimator = 'DWLS', group='UserLanguage')
# fit indices
fitMeasures(fit.configural)[indices]

# acceptable. Let's try metric invariance
fit.metric <- cfa(cfa.model, dat_mi, estimator = 'DWLS', group='UserLanguage',
                  group.equal='loadings')
fitMeasures(fit.metric)[indices]

# difference
fitMeasures(fit.metric)[indices] - fitMeasures(fit.configural)[indices]

# acceptable. Then, scalar
fit.scalar<- cfa(cfa.model, dat_mi, estimator = 'DWLS', group='UserLanguage',
                  group.equal=c('loadings','intercepts'))
fitMeasures(fit.scalar)[indices]

# difference
fitMeasures(fit.scalar)[indices] - fitMeasures(fit.metric)[indices]

# unacceptable. alignment necessary.
```
* configural invariance was not achieve despite good consistency
* try measurement alignment
```{r message=FALSE, warning=FALSE}
# extract parameters
par <- invariance_alignment_cfa_config(dat = dat_mi[,variables], 
                                       group = dat_mi$UserLanguage)

# do alignment
mod1 <- invariance.alignment(lambda = par$lambda, nu =
        par$nu, align.scale = c(0.2, 0.4), align.pow = c(0.25, 0.25))
# test performance
mod1$es.invariance['R2',]


# do itemwise test
# use parameters by Muthens .5 .5
cmod1<-invariance_alignment_constraints(mod1,.5,.5)
summary(cmod1)
```
* save result
* mod1 will be used for further correlational analysis
* with compliance, vaccine intent, misperception...
```{r message=FALSE, warning=FALSE}
save.image('1_conspiracy.RData')
```

